---
title: "assignment 7 :  Text Mining"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Group G3_9 (Lab 3) WARNING Executing the Rmd file might take a while (approx 3 mins on our machine) if you don't want to wait for this one could look just at the HTML file.

-   Camilla Kuijper (6000118)
-   Nikolas Anova (2505401)
-   Oscar Kromhof (8170045)

## Step 1 and 2: The IMDB dataset, Creating Document-term matrices (DTM) TF and TF-IDF, and Spliting Train and Test


```{r , echo=TRUE, results='hide', warning=FALSE, message=FALSE}

###### Libraries, IMDB dataset, etc #########
library(e1071)
library(text2vec)
library(tidyverse)
library(tm)
library(pROC)
library(Metrics)
options(expressions = 5e5)

# Reload movie_review dataset
IMDB <- movie_review

# Make Corpus from IMDB Review
corpus <- Corpus(VectorSource(IMDB$review))

# Set bounds
Bounds <- list(global = c(100,Inf))

# Set stopwords
ReviewStopwords <- c(stopwords(),"film","films","movie","movies")

################ TF #########################

# Creating DTM TF and Preprocessing Texts
IMDB_dtm_tf <- DocumentTermMatrix(corpus, control = list(bounds = Bounds, stopwords = ReviewStopwords, removePunctuation = T, removeNumbers = T, stemming = T))

# Converting DTM TF as input for model
df_tf <- data.frame(as.matrix(IMDB_dtm_tf))
df_tf <- df_tf %>% mutate(sentiment = IMDB$sentiment)

# Splitting TF into train and test
splits <- c(rep("train", 4000), rep("test", 1000))
df_tf_master <- df_tf %>% mutate(splits = sample(splits))

# Train for TF
df_tf_train <- df_tf_master %>% filter(splits == "train")
df_tf_train <- df_tf_train[,1:ncol(df_tf_train)-1]

# Test for TF
df_tf_test <- df_tf_master %>% filter(splits == "test")
df_tf_test <- df_tf_test[,1:ncol(df_tf_test)-1]


################ TF-IDF #####################

# Creating DTM TF-IDF and Preprocessing Texts
IMDB_dtm_tfidf <-  DocumentTermMatrix(corpus, control = list(bounds = Bounds, weighting = weightTfIdf, stopwords = ReviewStopwords, removePunctuation = T, removeNumbers = T, stemming = T)) 

# Converting DTM TF-IDF as input for model
df_tfidf <- data.frame(as.matrix(IMDB_dtm_tfidf))
df_tfidf <- df_tfidf %>% mutate(sentiment = IMDB$sentiment)

# Splitting TF-IDF into train and test
splits <- c(rep("train", 4000), rep("test", 1000))
df_tfidf_master <- df_tfidf %>% mutate(splits = sample(splits))

# Train for TF-IDF
df_tfidf_train <- df_tfidf_master %>% filter(splits == "train")
df_tfidf_train <- df_tfidf_train[,1:ncol(df_tfidf_train)-1]

# Test for TF-IDF
df_tfidf_test <- df_tfidf_master %>% filter(splits == "test")
df_tfidf_test <- df_tfidf_test[,1:ncol(df_tfidf_test)-1]


```


## Step 3 and 4: Choose 2 Classification tools; Train and Compare models 

```{r , echo=TRUE, results='hide', message=FALSE, warning=FALSE}
# We choose Support Vector Machines (SVM) and Naïve Bayes  for classification tools

################## TF for SVM ###############################

# Train Model
model <- svm(sentiment ~., data = df_tf_train, type = 'C')

# Predict test
Predict <- predict(model, newdata = df_tf_test )

```


```{r, echo=TRUE }
# Show table comparison between true value and prediction
true_value = df_tf_test$sentiment
Predict <- as.numeric(as.character(Predict))

table(true = true_value, predicted = Predict)

```


```{r, echo=TRUE }
# Calculate AUC 
auc_s <- roc(Predict,true_value)$auc
auc_s

```

```{r, echo=TRUE }
# Calculate Loss values
RMSE_s <- rmse(Predict, true_value)
RMSE_s
```


```{r , echo=TRUE, results='hide', message=FALSE, warning=FALSE}

################## TF for Bayes ###############################

# Train Model
model_B <- naiveBayes(sentiment ~., data = df_tf_train)
# Predict test
Predict_B <- predict(model_B, newdata = df_tf_test )

```


```{r, echo=TRUE }
# Show table comparison between true value and prediction
Predict_B <- as.numeric(as.character(Predict_B))

table(true = true_value, predicted = Predict_B)

```


```{r, echo=TRUE }
# Calculate AUC 
roc_B <- roc(Predict_B, true_value)
auc_B <- roc_B$auc
auc_B
```

```{r, echo=TRUE }
# Calculate Loss values
RMSE_B <- rmse(Predict_B, true_value)

RMSE_B
```


```{r , echo=TRUE, results='hide', message=FALSE, warning=FALSE}

################## TF-IDF for SVM ###############################

# Train Model
model_S_tfidf <- svm(sentiment ~., data = df_tfidf_train, type = 'C')

# Predict test
Predict_S_tfidf <- predict(model_S_tfidf, newdata = df_tfidf_test )

```


```{r, echo=TRUE }
# Show table comparison between true value and prediction
true_value = df_tfidf_test$sentiment

Predict_S_tfidf <- as.numeric(as.character(Predict_S_tfidf))

table(true = true_value, predicted = Predict_S_tfidf)

```


```{r, echo=TRUE }
# Calculate AUC 
auc_S_idf = roc(Predict_S_tfidf,true_value)$auc
auc_S_idf
```

```{r, echo=TRUE }
# Calculate Loss values
RMSE_S_idf = rmse(Predict_S_tfidf, true_value)

RMSE_S_idf
```


```{r , echo=TRUE, results='hide', message=FALSE, warning=FALSE}

################## TF-IDF for Bayes ###############################

# Train Model
model_B_tfidf <- naiveBayes(sentiment ~., data = df_tfidf_train)

# Predict test
Predict_B_tfidf <- predict(model_B_tfidf, newdata = df_tfidf_test)

```


```{r, echo=TRUE }
# Show table comparison between true value and prediction

Predict_B_tfidf <- as.numeric(as.character(Predict_B_tfidf))

table(true = true_value, predicted = Predict_B_tfidf)

```


```{r, echo=TRUE }
# Calculate AUC 
roc_B_tfidf <- roc(Predict_B_tfidf, true_value)
auc_B_tfidf <- roc_B_tfidf$auc

auc_B_tfidf
```

```{r, echo=TRUE }
# Calculate Loss values
RMSE_B_tfidf = rmse(Predict_B_tfidf, true_value)
RMSE_B_tfidf
```



## Step 5: Report & reflect

Comparison for SVM Model
```{r, echo = TRUE}
BoW <- c("TF", "TF-IDF")
AUC_SVM <- c(auc_s, auc_S_idf)
LossValue_SVM <- c(RMSE_s, RMSE_S_idf)

svm_comp <- data.frame(BoW, AUC_SVM, LossValue_SVM)

print (svm_comp)

```

Comparison for Bayes Model
```{r, echo = TRUE}
AUC_Bayes <- c(auc_B, auc_B_tfidf)
LossValue_Bayes <- c(RMSE_B, RMSE_B_tfidf)

bayes_comp <- data.frame(BoW, AUC_Bayes, LossValue_Bayes)

print (bayes_comp)

```
We note that in all cases the values for the AUC (>0.5). It is also the case that the SVM-method outperforms the NaiveBayes method by both metrics (AUC, and LossValue). We also get the result that the TF-IDF method for constructing the DTM matrix gives better estimates. So the results seem to be consistent with expected results.
